GeoSched: Minimizing Cost of Cloud Workloads in Geo-Distributed Data Centers

### 2015-04-01 doc/report/midterm/article.tex
mid term report outline

\section{Approaches }

We wish to consider all the major factors that impact the energy costs at the data center. Some of the factors and its impact are discussed in the below sub-section.

\begin{list2}
\item \textbf{Electricity pricing} We use the day-ahead hourly electricity prices to get the electricity cost of the data center which will enable us to provision workloads efficiently.\
\item \textbf{Energy source in data centers} To meet the energy requirements of data centers there is increasing adoption of renewable energy supply techniques (solar, wind). This has resulted in data centers being powered at least partially with green energy. \
\item \textbf{Cooling techniques employed} The other second generation solution of energy efficient data center is the use of air economizers in data centers. An air-side economizer brings outside air into a building and distributes it to the servers. \
\end{list2}

\section{Expected Milestones}

    \begin{tabular}{ | p{3cm} |l  |p{12cm}|  }
    \hline
    \bf{Item} & \bf{Deadline} & \bf{Description}   \\ \hline
    Study real-world and synthetic workloads & 10\textsuperscript{th} March,2015  & We have started studying workloads traces for google cluster-data which provides traces from a 12k-machine cell for one month duration in May 2011.  \\ \hline
    Data Center profile & 20\textsuperscript{th} March,2015  & In this process we will note the data center specific parameters such as electricity cost, available energy, economizer, cooling energy that is useful for simulating geo-distributed data centers. \\ \hline
    Feature Extraction & 25\textsuperscript{th} April,2015  & This phase will be identifying all the necessary features that contribute to the energy cost. These features will be used in the optimization of the energy cost \\ \hline
    Implementing Optimization technique & 5\textsuperscript{th} April,2015  & This is the most critical component and expected to consume major part of project. We will be building optimization techniques which is adaptive to workload characteristics and data center's resource capacity and electricity costs \\ \hline
    Evaluation & 7\textsuperscript{th} May,2015  & This phase we will be simulating data centers with previously gathered data center profile and using the optimization technique mentioned above \\ \hline

>>>>

\section{Cloud Workload }

\subsection{Workload Traces}

\subsection{Google Workload Trace}

\subsection{Custom Trace Format}

\section{Data Center Profiling }

Provide some introduction about out profiling stratergy

\subsection{Geo-Distributed Data Center}

\subsection{Profile Parameters}
\subsubsection{Temperature}
\subsubsection{Electricity Pricing}
\subsubsection{Energy Source}

\subsection{Air Economizer}

\section{Scheduler simulator}

Provide basic idea about our strategy

\subsection{Architecture}
Introduce cloudsim
\subsubsection{Components}
\subsubsection{Integration of traces and data center profile}
\subsubsection{Design}

\section{Scheduling Algorithm}

Provide basic idea about our strategy

\subsection{Features considered}
\subsubsection{Energy Cost Model}
%\subsubsection{Optimization Techiques}
%\subsubsection{Design}

\section{ Milestones}

    \begin{tabular}{ | p{3cm} |l  |p{11cm}|  }
    \hline
    \bf{Item} & \bf{Deadline} & \bf{Description}   \\ \hline
    Study real-world and synthetic workloads & 10\textsuperscript{th} March,2015  & We have started studying workloads traces for google cluster-data which provides traces from a 12k-machine cell for one month duration in May 2011.  \\ \hline
    Data Center profile & 20\textsuperscript{th} March,2015  & In this process we will note the data center specific parameters such as electricity cost, available energy, economizer, cooling energy that is useful for simulating geo-distributed data centers. \\ \hline
    Simulator design & 5\textsuperscript{th} April,2015  & Implement the simulator infrastructure for multi-datacenter environment.  \\ \hline
    Feature Extraction & 8\textsuperscript{th} April,2015  & This phase will be identifying all the necessary features that contribute to the energy cost. These features will be used in the optimization of the energy cost \\ \hline
    Implementing Optimization technique & 25\textsuperscript{th} April,2015  & This is the most critical component and expected to consume major part of project. We will be building optimization techniques which is adaptive to workload characteristics and data center's resource capacity and electricity costs \\ \hline
    Evaluation & 7\textsuperscript{th} May,2015  & This phase we will be simulating data centers with previously gathered data center profile and using the optimization technique mentioned above \\ \hline
